\textsf{Are large language models superhuman chemists?}

### 2024-10-28 src/tex/ms.tex
fix: fix orcid and add acknowledgments (#83)
Co-authored-by: vgvinter <vicky@INCAR-162.campus.csic.es>

\begin{figure}[!htb]
    \centering
    \includegraphics[width=\textwidth]{figures/CB_OVERVIEW_FIG_V1.pdf}
    \caption{\textbf{Distribution of topics and required skills.} This circular plot illustrates the distribution of questions across various chemistry topics, along with the primary skills required to address them. The topics were manually classified, showing a varied representation across different aspects of chemistry. Each topic is associated with a combination of three key skills: Calculation, Reasoning, and Knowledge, as indicated by the colored bars. \chembench samples diverse topics and diverse skills, setting a high bar for \glspl{llm} to demonstrate human-competitive performance across a wide range of chemistry tasks.}
    \label{fig:corpus}
\end{figure}

@@

\begin{table}[!h]
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data on GitHub. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus. Note that the chemical preference questions are the main corpus of the semi-automatically generated group with 1001 questions of the total 1752.}
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}

@@

>>>>

\begin{figure}[!htb]
    \centering
    \includegraphics[width=\textwidth]{figures/CB_OVERVIEW_FIG_V2.pdf}
    \caption{\textbf{Distribution of topics and required skills.} This circular plot illustrates the distribution of questions across various chemistry topics, along with the primary skills required to address them. The topics were manually classified, showing a varied representation across different aspects of chemistry. Each topic is associated with a combination of three key skills: Calculation, Reasoning, and Knowledge, as indicated by the colored bars. \chembench samples diverse topics and diverse skills, setting a high bar for \glspl{llm} to demonstrate human-competitive performance across a wide range of chemistry tasks.}
    \label{fig:corpus}
\end{figure}

@@

\begin{table}[!h]
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data on GitHub. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus.}
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}

@@

M.R.G.\ and M.V.G.\ acknowledge financial support from the Spanish Agencia Estatal de Investigaci\'{o}n (AEI) through grants TED2021-131693B-I00 and CNS2022-135474, funded by MICIU/AEI/10.13039/501100011033 and by the European Union NextGenerationEU/PRTR. M.V.G.\ acknowledges support from the Spanish National Research Council (CSIC) through Programme for internationalization i-LINK 2023 (Project ILINK23047).
